Deep learning for geophysics

### 2023-10-10 manuscript.tex
Further fix cross references
Fix incorrect inserted page numbering

\newpage{}
% \subfile{authorship_declaration}
\includepdf[pages=-]{authorship_declaration_signed.pdf}

@@

\chapter{Introduction}
% \subfile{intro}
% \includepdf[pages=-]{intro.pdf}
\include{intro}

\chapter{Magnetic Grid Resolution Enhancement using Machine Learning}
\label{paper1}
This chapter has been reproduced from the following peer reviewed publication. Formatting has been adjusted for consistency.

@@

\chapter{Super-resolution of Aeromagnetic Survey Data}
\label{paper2}
% \includepdf[pages=-]{paper2.pdf}
% \subfile{paper2}
\include{paper2}

\chapter{Implicit Neural Representation for Potential Field Geophysics}
\label{paper3}
% \includepdf[pages=-]{paper3.pdf}
% \subfile{paper3}
\include{paper3}

>>>>

\newpage{}
% \subfile{authorship_declaration}
% Fix incorrect page numbering
\includepdf[pages=-,templatesize={595.276pt}{841.89pt},nup=1x1,scale=1,clip,trim=5mm 36.5mm 5mm 20mm,fitpaper=true,pagecommand={\pagestyle{plain}}]{authorship_declaration_signed.pdf}

@@

\chapter{Introduction}
\label{ch:intro}
% \subfile{intro}
% \includepdf[pages=-]{intro.pdf}
\include{intro}

\chapter{Magnetic Grid Resolution Enhancement using Machine Learning}
\label{ch:paper1}
This chapter has been reproduced from the following peer reviewed publication. Formatting has been adjusted for consistency.

@@

\chapter{Super-resolution of Aeromagnetic Survey Data}
\label{ch:paper2}
% \includepdf[pages=-]{paper2.pdf}
% \subfile{paper2}
\include{paper2}

\chapter{Implicit Neural Representation for Potential Field Geophysics}
\label{ch:paper3}
% \includepdf[pages=-]{paper3.pdf}
% \subfile{paper3}
\include{paper3}
